Computing Restricted Isometry Constants via Mixed-Integer Semidefinite Programming

### 2016-08-29 RIP-MISDP-Paper/IEEE_RIP-MISDP_peerreview.tex
use bar instead of check in model to distinguish variable and given solution
PAPER: emphasize that the extreme point should attain the optimal objective in the rank-1-proof

  Let $(X^\star, z^\star)$ be an optimal solution to \eqref{MISDP} with
  $\ell \define \sum_{i=1}^n z^\star_i \leq k$. Let $T \define \{i_1, i_2,
  \dots, i_\ell\}$ be the support of $z^\star$, and define $\check{A} =
  (A_{i_1}, A_{i_2}, \dots, A_{i_\ell})$ to be the submatrix of~$A$ formed by
  the columns indexed by~$T$. Then consider
  \begin{equation}\label{Proj}
   \begin{aligned}
    \min \quad & \Tr(\check{A}\T \check{A} \check{X}), \\
    \text{s.t.} \quad & \Tr(\check{X}) = 1, \\
    & \check{X} \succeq 0,\; \check{X} \in S_\ell.
   \end{aligned}
  \end{equation}

@@

  Let $\check{X}$ be an extreme point of \eqref{Proj} (since the set of
  optimal points of~\eqref{Proj} is nonempty, convex, and compact, such a
  point exists, see~\cite[Corollary 18.5.1]{Roc70}). Defining the face $F =
  \{\check{X}\}$ and applying Theorem~\ref{patakiLemma} on \eqref{Proj}
  gives
  \begin{equation*}
    \tfrac{1}{2} \Rk(\check{X}) \cdot (\Rk(\check{X})+1) \leq \tilde{m} + dim(F) = 1 + 0 = 1,
  \end{equation*}
  since there are $\tilde{m} = 1$ linear constraints. Since $\check{X} = 0$
  is infeasible for $\Tr(X) = 1$, it follows that $\Rk(\check{X}) = 1$,
  which can then be lifted to an optimal solution of \eqref{MISDP} of rank
  one.
\end{proof}

>>>>

  Let $(X^\star, z^\star)$ be an optimal solution to \eqref{MISDP} with
  $\ell \define \sum_{i=1}^n z^\star_i \leq k$. Let $T \define \{i_1, i_2,
  \dots, i_\ell\}$ be the support of $z^\star$, and define $\bar{A} =
  (A_{i_1}, A_{i_2}, \dots, A_{i_\ell})$ to be the submatrix of~$A$ formed by
  the columns indexed by~$T$. Then consider
  \begin{equation}\label{Proj}
   \begin{aligned}
    \min \quad & \Tr(\bar{A}\T \bar{A} \bar{X}), \\
    \text{s.t.} \quad & \Tr(\bar{X}) = 1, \\
    & \bar{X} \succeq 0,\; \bar{X} \in S_\ell.
   \end{aligned}
  \end{equation}

@@

  Let $\check{X}$ be an extreme point of \eqref{Proj} that attains the
  optimal objective value (since the set of
  optimal points of~\eqref{Proj} is nonempty, convex, and compact, such a
  point exists, see~\cite[Corollary 18.5.1]{Roc70}). Defining the face $F =
  \{\check{X}\}$ and applying Theorem~\ref{patakiLemma} on \eqref{Proj}
  gives
  \begin{equation*}
    \tfrac{1}{2} \Rk(\check{X}) \cdot (\Rk(\check{X})+1) \leq \tilde{m} + dim(F) = 1 + 0 = 1,
  \end{equation*}
  since there are $\tilde{m} = 1$ linear constraints. Since $\check{X} = 0$
  is infeasible for $\Tr(X) = 1$, it follows that $\Rk(\check{X}) = 1$,
  which can then be lifted to an optimal solution of \eqref{MISDP} of rank
  one.
\end{proof}
